Identifying regime transitions for water governance at the Yellow River Basin, China

### 2023-10-07 paper/main/04_discussion.tex
docs(paper): :memo: update discussion according to R1's suggestion

% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water cycle in order to maintain the provisioning (larger) and non-provisioning water (less).
At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
In an analogy at a global scale, the resource challenges, represented by water shortage and water supplying difficulties, are mainly faced by undeveloped and developing basins~\cite{allan2019,speed2013,liu2012}.
Highly-controlled and developed basins (especially for transboundary rivers) must mainly resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

>>>>

% 总体而言，长江流域的水治理是“改善供给、转变治理、增强适应”的水社会循环总体转型中最突出的例子之一。
In general, water governance of the YRB is among the most prominent example in the widespread transition to a hydrosocial cycle -``improving supply, transforming governance, and enhancing adaptation''.
To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water cycle in order to maintain the provisioning (larger) and non-provisioning water (less).
At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
% 在黄河流域具体来说，其表现为国家的宣传口号从战胜自然和保护环境变成了人水和谐，但仍不得不用行政手段处理用水争端
The Yellow River basin's challenges as an example, represented by the shift in national narratives from conquering nature for economy and eliminating pollution to stressing of harmonious human-water, increased the importance of administrative measures in resolving water-related disputes.
It demonstrates again that highly-controlled and developed basins (especially for transboundary rivers) must resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures~\cite{unep-dhi2016,mirumachi2015}.
Linking regime shifts to the governance challenges, the implementation of IWGI thus offers a comprehensive and straightforward way to interpret the intertwines between water governance and the hydrosocial transition.

### 2023-10-07 paper/response_letter/source/reviewer_1.tex
fix(paper): :pencil2: natural water processes -> natural water cycle
docs(paper): :memo: update discussion according to R1's suggestion

@@

@@

>>>>

\AR{} Thank you for bringing to our attention the ambiguity associated with the term ``natural water processes''. To enhance clarity and precision, we have revised this phrase to ``natural water cycle'' in our updated manuscript.

@@

\AR{} We have incorporated the specific examples you suggested into the revised manuscript to provide a clearer illustration of the water governance transition in the Yellow River basin. We are grateful for your insightful recommendation.

\begin{quote}
	% 以黄河流域所面临的挑战为例，国家叙事从经济征服自然、消除污染到强调人水和谐的转变，增加了行政措施在解决与水有关的纠纷中的重要性。
	The Yellow River basin's challenges as an example, represented by the shift in national narratives from conquering nature for economy and eliminating pollution to stressing of harmonious human-water, increased the importance of administrative measures in resolving water-related disputes.
\end{quote}

@@

\AR{} We have reviewed and carefully considered your feedback. We have removed the statements that were not strongly correlated with the core content of our study. After then, we linked the YRB's example by the interpretation:

\begin{quote}
	% 它再次表明，高度控制和开发的流域(特别是跨界河流)必须解决结构性挑战，例如水争端或缺乏公平，并且可能迫切需要新的灵活、有效的社会政治治理结构。
	It demonstrates again that highly-controlled and developed basins (especially for transboundary rivers) must resolve structural challenges, such as water disputes or lack of equity, and may be in urgent need of novel flexible, efficient sociopolitical governance structures.
\end{quote}
